Molecular Analysis

### 2023-10-17 analysis/mol_analysis.Rmd
add posterior probabilities to plots

pos_tot_pl <- ggplot(mapping = aes(y = n, x = 1, fill = variable)) +
  geom_bar(data = df_pos_tot, stat = "identity", position = position_stack(reverse = T), width = .5) +
  geom_text(data = df_pos_tot %>% mutate(n_lab = paste0(variable, ": ", n)), 
            mapping = aes(label = n_lab), 
            size = 8 / cm(1), position = position_stack(vjust = 0.5, reverse = T), color = "white") +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_color_manual(values = wes_palette("IsleofDogs1")) +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = expansion(mult = c(0.1,0.3))) +
  labs(y = "Number of positive samples", fill = "Virus", title = "a") +
  theme_custom() +
  theme(panel.grid = element_blank(),
        plot.title.position = "plot",
        legend.position = "none",
        # legend.title = element_blank(),
        # legend.key.width = unit(.3, "cm"),
        # legend.key.height = unit(.1, "cm"),
        axis.title.x = element_blank(),
        axis.line.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  guides(fill = guide_legend(nrow = 1))

@@

save_plot(pos_tot_pl, 
          "../results/mol-data/saliva-distribution.pdf",
          "../results/mol-data/saliva-distribution.eps",
          w = 3.25, h = 20)
```

@@

save_plot(tnet_pl, 
          pdf_file = "../results/mol-data/network-plot.pdf", 
          eps_file = "../results/mol-data/network-plot.eps", 
          w = 12.25, h = 20)
```

>>>>

pos_tot_pl <- ggplot(mapping = aes(y = n, x = 1, fill = variable)) +
  geom_bar(data = df_pos_tot, stat = "identity", position = position_stack(reverse = T), width = .5) +
  geom_text(data = df_pos_tot %>% mutate(n_lab = paste0(variable, ": ", n)), 
            mapping = aes(label = n_lab), 
            size = 8 / cm(1), position = position_stack(vjust = 0.5, reverse = T), color = "white") +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_color_manual(values = wes_palette("IsleofDogs1")) +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = expansion(mult = c(0.1,0.3))) +
  labs(y = "Number of positive saliva samples", fill = "Virus", title = "a") +
  theme_custom() +
  theme(panel.grid = element_blank(),
        plot.title.position = "plot",
        legend.position = "none",
        # legend.title = element_blank(),
        # legend.key.width = unit(.3, "cm"),
        # legend.key.height = unit(.1, "cm"),
        axis.title.x = element_blank(),
        axis.line.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  guides(fill = guide_legend(nrow = 1))

@@

save_plot(pos_tot_pl, 
          "../results/mol-data/saliva-distribution.pdf",
          "../results/mol-data/saliva-distribution.eps",
          w = 3.25, h = 19)
```

@@

save_plot(tnet_pl, 
          pdf_file = "../results/mol-data/network-plot.pdf", 
          eps_file = "../results/mol-data/network-plot.eps", 
          w = 12.25, h = 19)
```
